Time Series Bootstrapping For Solar Current

### 2021-12-05 deliverables/paper.Rmd
Added Bootstrapping
Hear I wrote the code for bootstrapping using blocks of length 4 and 12 based on average peak hours. I cannot figure out how to add the data from the python scripts, I don't use python, studio together. Everything should be set up though where I can quickly change the data calls once I can access it. I've also added some comments depicting some other approaches I can take.

>>>>

```{r functions}
np <- function(x, l, b) {
  blocks <- matrix(NA, nrow = b, ncol = l)
  for(i in 1:length(x)) {
    blocks[i,] <- x[(i-1)*l+1:(i*l)]
  }
  blocks
}

nbb <- function(x, l) {
  B <- 10000
  b <- floor(length(x)/l)
  theta_hat_star_nbb <- rep(NA, B)
  nb_blocks <- np(x, l, b)
  for(i in 1:B) {
    # sample blocks
    idx <- sample(1:b, b, replace = TRUE)
    theta_hat_star_nbb[i] <- mean(x[idx, ])
  }
  ggplot() +
    geom_histogram(aes(theta_hat_star_nbb))

  st.d <- sd(theta_hat_star_nbb)
  bias <- mean(theta_hat_star_nbb) - mean(x)

  print(paste("The standard deviation with ", l, " blocks is: ", st.d, ". \n The bias is: ",
              bias))
}

```

```{r sampling}
#B1 <- df[df$Hour == c(7:10),]$current_output # Hours before peak
#B2 <- df[df$Hour == c(11:14),]$current_output # Peak hours
#B3 <- df[df$Hour == c(15:18),]$current_output # Hours after peak

hours <- df[df$Hour == c(7:18),]$current_output
nbb(hours, 4) # in order to make b blocks I would need to solve for b = [n/l] (floor) where n is the length of our data and l is 4, so make nbb call l instead of b

nbb(hours, 12)

# Could also block instead by hours but by total current output. Peak hours would be a frame around the highest output and then hours before and after would coincide with that. This would cause the hours to potentially be different based on the season/month as months that get dark earlier could see peak hours earlier in the day.

#dpeak <- c(B1,B2,B3)
```
